---
title: "dm_mas405_final"
author: "Dominique McDonald"
date: '2022-05-18'
output: pdf_document
---

Using the following as a guide: https://www.red-gate.com/simple-talk/databases/sql-server/bi-sql-server/text-mining-and-sentiment-analysis-with-r/




Installing packages for text analysis.
```{r}
# install.packages("tm")  # for text mining
# install.packages("SnowballC") # for text stemming
# install.packages("wordcloud") # word-cloud generator
# install.packages("RColorBrewer") # color palettes
# install.packages("syuzhet") # for sentiment analysis
# install.packages("ggplot2")
```

```{r, warning= FALSE}
#Now load those bad boys


library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(syuzhet)
library(ggplot2)
library(RMySQL)
```





```{r}
#connecting to my db

drv <- dbDriver("MySQL")
xdbsock <- ""


#############
xdbuser <- Sys.getenv("MAS405_AWS_DOMINIQUE_DB_ROUSER_USER")
xpw     <- Sys.getenv("MAS405_AWS_DOMINIQUE_DB_ROUSER_PW")
xdbname <- Sys.getenv("MAS405_AWS_DOMINIQUE_DB_ROUSER_DBNAME")
xdbhost <- Sys.getenv("MAS405_AWS_DOMINIQUE_DB_ROUSER_HOST")
xdbport <- as.integer( Sys.getenv("MAS405_AWS_DOMINIQUE_DB_ROUSER_PORT") )

# xdbuser <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_USER")
# xpw     <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PW")
# xdbname <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_DBNAME")
# xdbhost <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_HOST")
# xdbport <- as.integer( Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PORT") )


con <-
dbConnect(
drv,
user=xdbuser,
password=xpw,
dbname=xdbname,
host=xdbhost,
port=xdbport,
unix.sock=xdbsock
)


dbListTables(con)

```







```{r}
#getting the data

#Decided to use OG sonnets instead of pseudo sonnets
#qry1 <- "SELECT * FROM sonnets"

qry1 <- "SELECT * FROM OG"

x <- dbGetQuery(con, qry1)
colnames(x) <- c("row_names", "Sonnets") 
head(x)



```


```{r}
#need to load vector of text objects as a corpus
#VectorSource() interprets each element of a vec as a document
x_text <- Corpus(VectorSource(x$Sonnets))


x_text
```
In the future no need to use content_transformer(). That is easy to do in base and it drops documents(???) 
```{r}
#Replacing "/", "@" and "|" with space
toSpace <- content_transformer(function (y , pattern ) gsub(pattern, " ", y))
#to_e <- content_transformer(function (y , pattern ) gsub(pattern, "e", y)) wasnt' helpful
x_text <- tm_map(x_text, toSpace, "/")
x_text <- tm_map(x_text, toSpace, "@")
x_text <- tm_map(x_text, toSpace, "\\|")
x_text <- tm_map(x_text, to_e, "’")
# Convert the text to lower case
#x_text <- tm_map(x_text, content_transformer(tolower))
# Remove numbers
x_text <- tm_map(x_text, removeNumbers)
# Remove english common stopwords
x_text <- tm_map(x_text, removeWords, stopwords("english"))
# Remove your own stop word
# specify your custom stopwords as a character vector

x_text <- tm_map(x_text, removeWords, c("thi", "thee", "thou", "may", "still", "thus", "though", "can", "will", "hath", "doth", "thine", "like", "much", "let",
                                        "upon", "from", "dost", "shall", "thy")) 
# Remove punctuations
x_text <- tm_map(x_text, removePunctuation)
# Eliminate extra white spaces
x_text <- tm_map(x_text, stripWhitespace)
# Text stemming - which reduces words to their root form
#x_text <- tm_map(x_text, stemDocument)

x_text #NO DOCUMENTS DROPPED

```
The document term matrix just contains all the words in your "documents" and their frequencies and maybe their stem, gotta check
```{r}
# Build a term-document matrix
x_text_dtm <- TermDocumentMatrix(x_text)

x_text_dtm
#number of total terms is the non sparse entries

mat_dtm <- as.matrix(x_text_dtm)
# mat_dtm
# Sort by decreasing value of frequency
dtm_v <- sort(rowSums(mat_dtm),decreasing=TRUE)
dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
# Display the top 5 most frequent words
head(dtm_d, 50)


```

```{r}
#generate word cloud
set.seed(314)
wordcloud(words = dtm_d$word, freq = dtm_d$freq, min.freq = 5,
          max.words=100, random.order=FALSE, rot.per=0.20, 
          colors=brewer.pal(8, "Dark2"))
head(dtm_v)
##play around with shapes

```



```{r}
# Find associations 
findAssocs(x_text_dtm, terms = c("eyes","sweet","love", "heart", "time"), corlimit = 0.4)			




```


```{r}
# Find associations for words that occur at least 50 times
findAssocs(x_text_dtm, terms = findFreqTerms(x_text_dtm, lowfreq = 50), corlimit = 0.40)

```

```{r}

# regular sentiment score using get_sentiment() function and method of your choice
# please note that different methods may have different scales
#### NOTE YOU DO NOT HAVE TO USE A CORPUS FOR THE SYUZHET PACKAGE HERE. THIS IS JUST THE VECTOR OF SONNETS
s_vector <- get_sentiment(x$Sonnets, method="syuzhet") 
# see the first row of the vector
head(s_vector, n = 10)
# see summary statistics of the vector
summary(s_vector)
hist(s_vector, col = "pink") #normal distribution 

```
```{r}

#simple_plot(s_vector) #dont think this will be useful
head(dtm_d)
num_terms <- length(x_text_dtm$i); num_terms #total number of terms - 7611
nTerms(x_text_dtm) # unique terms in sonnets - 3089
head(Terms(x_text_dtm)) #just a list of all the terms that show up

prop_terms<-  dtm_d$freq/num_terms; head(prop_terms)

dtm_prop <- cbind(dtm_d, prop_terms)



```




Looking into other data sets


We have decided not to use the netflix data, but keeping this just in case.
```{r}

qry1 <- "SELECT * FROM netflix"

netflix <- dbGetQuery(con, qry1)

head(netflix)
names(netflix)
head(netflix$description)#probably more useful
head(netflix$genres) #not gonna be helpful for us really

```




```{r}
#need to load vector of text objects as a corpus
#VectorSource() interprets each element of a vec as a document
netflix_text <- Corpus(VectorSource(netflix$description))


netflix_text
```




```{r}
# #Replacing "/", "@" and "|" with space
# toSpace <- content_transformer(function (y , pattern ) gsub(pattern, " ", y))
# #to_e <- content_transformer(function (y , pattern ) gsub(pattern, "e", y)) wasnt' helpful
# netflix_text <- tm_map(netflix_text, toSpace, "/")
# netflix_text <- tm_map(netflix_text, toSpace, "@")
# netflix_text <- tm_map(netflix_text, toSpace, "\\|")
# netflix_text <- tm_map(netflix_text, to_e, "’")
# # Convert the text to lower case
# netflix_text <- tm_map(netflix_text, content_transformer(tolower))
# # Remove numbers
# netflix_text <- tm_map(netflix_text, removeNumbers)
# # Remove english common stopwords
# netflix_text <- tm_map(netflix_text, removeWords, stopwords("english"))
# # Remove your own stop word
# # specify your custom stopwords as a character vector
# 
# netflix_text <- tm_map(netflix_text, removeWords, c("thi", "thee", "thou", "may", "still", "thus", "though", "can", "will", "hath", "doth", "thine", "like", "much", "let",
#                                         "upon", "from", "dost", "shall", "thy")) 
# # Remove punctuations
# netflix_text <- tm_map(netflix_text, removePunctuation)
# # Eliminate extra white spaces
# netflix_text <- tm_map(netflix_text, stripWhitespace)
# # Text stemming - which reduces words to their root form
# #x_text <- tm_map(x_text, stemDocument)
# 
# netflix_text #NO DOCUMENTS DROPPED

```



```{r}
# Build a term-document matrix
# netflix_text_dtm <- TermDocumentMatrix(netflix_text)
# netflix_mat_dtm <- as.matrix(netflix_text_dtm)
# #head(netflix_mat_dtm)
# # Sort by decreasing value of frequency
# netflix_dtm_v <- sort(rowSums(netflix_mat_dtm),decreasing=TRUE)
# netflix_dtm_d <- data.frame(word = names(netflix_dtm_v),freq=netflix_dtm_v)
# # Display the top 5 most frequent words
# head(netflix_dtm_d, 50)


```






```{r}
# #generate word cloud
# set.seed(314)
# wordcloud(words = netflix_dtm_d$word, freq = netflix_dtm_d$freq, min.freq = 10,
#           max.words=100, random.order=FALSE, rot.per=0.20, 
#           colors=brewer.pal(8, "Dark2"))
# 
# ##play around with shapes



```



```{r}
# netflix_vector <- get_sentiment(netflix$description, method="syuzhet")
# # see the first row of the vector
# head(netflix_vector, n = 10)
# # see summary statistics of the vector
# summary(netflix_vector)
# hist(netflix_vector, col = "blue2", breaks = 20) #normal distribtion 
# 
# cor(netflix_vector, netflix$imdb_score)
# 
# summary(netflix$imdb_score)
```

########## WORKING WITH ARTIST DATA NOW #############

```{r}

#DONT FORGET TO UNCOMMENT THESE LINES****
 qry1 <- "SELECT * FROM Lyrics"
 artist <- dbGetQuery(con, qry1)

head(artist, n = 2)
dim(artist)
colnames(artist) <- c("ID","Artist", "songs")

View(artist)

######THERE ARE DUPLICATES IN THE DATA REMEMBER TO COME BACK AND CHANGE THEM! RIGHT NOW I AM JUST FOCUSED ON WRITING THE LOOP#######
#specifically observations 41 & 42

#need to look into words within []


# test<- artist$songs[1]
# library(stringr)
# str_extract_all(pattern = "^\\[") #use this to get rid of words in brackets


```


Gonna write a loop that performs key word extraction on each artist's work. 
Result: - A list containing a df for each artists.
        - Each artist's df will contain: top 10 keywords, frequencies, proportions
        
```{r}
#creating list that will be populated by loop
artist_keyword <- list()
artist_keyword


artist_text <- Corpus(VectorSource(artist$songs)); artist_text

for(i in 1:length(artist$Artist)){
 
  kw <- rep(NA, 10)
  frq <- rep(NA, 10)
  prp <- rep(NA, 10)
  temp_mat <- cbind(kw, frq, prp)
  artist_keyword[[i]] <-as.data.frame(temp_mat) # ea. element will be df with 10 rows and 3 columns, chose not to                                                                                           # include artist because it would just be repeated, but could be                                                                                            # useful. discuss???
  colnames(artist_keyword[[i]]) <- c("keyword","frequency", "proportion" )
  
  art_doc <- artist_text[i]
  
  #Replacing "/", "@" and "|" with space
  toSpace <- content_transformer(function (y , pattern ) gsub(pattern, " ", y))
  #to_e <- content_transformer(function (y , pattern ) gsub(pattern, "e", y)) wasnt' helpful
  art_doc <- tm_map(art_doc, toSpace, "/")
  art_doc <- tm_map(art_doc, toSpace, "@")
  art_doc <- tm_map(art_doc, toSpace, "\\|")
  #art_doc <- tm_map(art_doc, to_e, "’")
  # Convert the text to lower case
  art_doc <- tm_map(art_doc, content_transformer(tolower))
  # Remove numbers
  art_doc <- tm_map(art_doc, removeNumbers)
  # Remove english common stopwords
  art_doc <- tm_map(art_doc, removeWords, stopwords("english"))
  # Remove your own stop word
  # specify your custom stopwords as a character vector
  
  art_doc <- tm_map(art_doc, removeWords, c("aint", "ooh", "thou", "never", "yeah", "hey", "though", "just", "will", "dont", "gonna", "can",                                                            "let", "thing", "every", "cause", "Since", "along",  "always", "many" , "eighteen", "hundred",
                                            "upon", "from", "nah", "shall", "now", "one", "two", "cant", "dont", "wont", "like", "much")) 
  # Remove punctuations
  art_doc <- tm_map(art_doc, removePunctuation)
  # Eliminate extra white spaces
  art_doc <- tm_map(art_doc, stripWhitespace)
  # Text stemming - which reduces words to their root form
  #x_text <- tm_map(x_text, stemDocument)
  
  #art_doc #NO DOCUMENTS DROPPED

  art_doc_dtm <- TermDocumentMatrix(art_doc)
  

  #art_doc_dtm
  #number of total terms is the non sparse entries
  
  artist_mat_dtm <- as.matrix(art_doc_dtm)
  # mat_dtm
  # Sort by decreasing value of frequency
  artisit_dtm_v <- sort(rowSums(artist_mat_dtm),decreasing=TRUE)
  artist_dtm_d <- data.frame(word = names(artisit_dtm_v),freq=artisit_dtm_v)
  artist_dtm_d
  
  
  artist_keyword[[i]]$keyword[1:10] <- artist_dtm_d$word[1:10] #populating keywords
  artist_keyword[[i]]$frequency[1:10] <- artist_dtm_d$freq[1:10]; artist_keyword #populating frequencies
  
  art_num_terms <- length(art_doc_dtm$i); art_num_terms #total number of terms
  artist_keyword[[i]]$proportion[1:10] <- artist_dtm_d$freq[1:10]/art_num_terms #populating proportions
  
  
}

names(artist_keyword) <- artist$Artist
artist_keyword[28] #look at the data frame one at a time otherwise your computer won't like you



```





