 ---
title: "Sentiment Analysis on OG Sonnets and Artists"
author: "Mariana Gonzalez Castro"
date: "5/22/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(RMySQL)
library(DBI)

library(dplyr)
library(stringr)

library(tm)
library(syuzhet)
library(wordcloud)

library(cluster)
library(factoextra)

library(ggplot2)
```


```{r}
drv <- dbDriver("MySQL")
xdbsock <- ""


#############
xdbuser <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_USER")
xpw     <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PW")
xdbname <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_DBNAME")
xdbhost <- Sys.getenv("MAS405_AWS_MY_DB_ADMIN_HOST")
xdbport <- as.integer( Sys.getenv("MAS405_AWS_MY_DB_ADMIN_PORT") )



con <-
  dbConnect(
    drv,
    user=xdbuser,
    password=xpw,
    dbname=xdbname,
    host=xdbhost,
    port=xdbport,
    unix.sock=xdbsock
  )


dbListTables(con)

original_sonnets <- dbGetQuery(con, "SELECT * FROM OG")

#dbWriteTable(con, name = "artists_complete", artists_complete, overwrite=T)

artists_complete <- dbGetQuery(con, "SELECT * FROM artists_complete")

dbDisconnect(con)


```

## Original Sonnets

**Data Cleanup** 
```{r}
#*sigh* Idk why dbWriteTable creates a column of row numbers
og <- select(original_sonnets,-c(1)) 

og[1,1] #it appears that the special characters are back again...so stubborn

#R, wtf is up with the column name? 
og <- rename(og, "og_sonnets" = "rep.NA..154.")

og <- 
  og %>% 
  mutate_at("og_sonnets", str_replace, "’", "\'") 

og_sonnets <- data.frame(matrix(ncol=1,nrow=154, 
                                 dimnames=list(NULL, "Sonnets")))

#I manually removed the punctuation except for apostrophes
n <- 154
for (i in 1:154) {
  og_sonnets[i,]<- gsub("[,.;:?!]", "", og[i,1])
  rbind(og_sonnets[i,])
} 

og_sonnets[1,1]

```


**Sentiment Analysis** 
og_sonnets is the dataframe we are working with. (I know I use too many names lol)
```{r}
#create an empty dataframe
emotions <- data.frame(matrix(ncol=10,nrow=0, dimnames=list(NULL, 
      c("anger", "anticipation", "disgust", "fear", "joy", "sadness", 
        "surprise", "trust", "negative", "positive"))))

n <- 154

#ran a for loop to conduct sentiment analysis to each individual sonnet
for (i in 1:n) {
  emotions[i,]<- get_nrc_sentiment(og_sonnets[i,1])
  rbind(emotions[i,])
}

head(emotions) 

#should write this into my db...at some point


```

```{r}
#Very ROUGH barplot 
s <- colSums(emotions)
ss <- s[c("anger", "anticipation", "disgust", "fear", "joy", "sadness", 
        "surprise", "trust")]
sss <- s[c("negative", "positive")]
barplot(ss,
        main = "Frequency of Each Emotion",
        las = 2,
        col = terrain.colors(15))
barplot(sss,
        main = "Frequency of Positive and Negative Sentiments",
        las = 2,
        col = rainbow(15))


```

```{r}
#visualize what words fell under the 8 emotion categories

all = c(
  paste(og_sonnets[emotions$anger > 0,], collapse=" "),
  paste(og_sonnets[emotions$anticipation > 0,], collapse=" "),
  paste(og_sonnets[emotions$disgust > 0,], collapse=" "),
  paste(og_sonnets[emotions$fear > 0,], collapse=" "),
  paste(og_sonnets[emotions$joy > 0,], collapse=" "),
  paste(og_sonnets[emotions$sadness > 0,], collapse=" "),
  paste(og_sonnets[emotions$surprise > 0,], collapse=" "),
  paste(og_sonnets[emotions$trust > 0,], collapse=" ")
)

all <- removeWords(all, stopwords("english"))

all <- removeWords(all, c("thi", "thee", "thou", "may", "still", "thus", 
                          "though", "can", "will", "hath", "doth", "thine", 
                          "like", "much", "let", "upon", "from", "dost", 
                          "shall", "thy"))
all <- stripWhitespace(all)
all <- removeNumbers(all)

# create corpus
corpus = Corpus(VectorSource(all))

# create term-document matrix
tdm = TermDocumentMatrix(corpus)
#
# convert as matrix
tdm = as.matrix(tdm)
#
# add column names
colnames(tdm) = c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 
                  'surprise', 'trust')
comparison.cloud(tdm, random.order=F,
                 title.colors = c("#00B2FF", "red", "#FF0099", "#6600CC", 
                                  "green", "orange", "blue", "brown"), 
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", 
                            "orange", "blue", "brown"),
                 title.size=1, max.words=400,scale=c(2, 0.4),rot.per=0.5)

```



```{r}
#something doesn't feel right...checking the sentiments now

sentiments = c(
  paste(og_sonnets[emotions$negative > 0,], collapse=" "),
  paste(og_sonnets[emotions$positive > 0,], collapse=" ")
)

sentiments <- removeWords(sentiments, stopwords("english"))

sentiments <- removeWords(sentiments, c("thi", "thee", "thou", "may", "still", "thus", "though", "can", "will", "hath", "doth", "thine", "like", "much", "let",
                                        "upon", "from", "dost", "shall", "thy"))
sentiments <- stripWhitespace(sentiments)
sentiments <- removeNumbers(sentiments)

# create corpus
corpus2 = Corpus(VectorSource(sentiments))

# create term-document matrix
tdm2 = TermDocumentMatrix(corpus2)
#
# convert as matrix
tdm2 = as.matrix(tdm2)
#
# add column names
colnames(tdm2) = c('negative', 'positive')
comparison.cloud(tdm2, random.order=F,
                 title.colors = c("red","#00B2FF"), 
                 colors = c("red","#00B2FF"),
                 title.size=1, max.words=400,scale=c(2, 0.4),rot.per=0.5)

```



```{r}
total <- rowSums(tdm)
termdoc <- cbind(tdm, total)
head(termdoc)

total2 <- rowSums(tdm2)
termdoc2 <- cbind(tdm2, total2)
head(termdoc2)

#findFreqTerms(m, lowfreq = 300)
#findMostFreqTerms(m)
```


## Clustering Algorithm

I want to attempt a k-means clustering and see what happens. I am going to first determine the ideal number of clusters by checking how much variance of the data would be explained with the total number of clusters. 

```{r}
#will be applying k-means clustering to the Term Document Matrix or tdm 
k <- 8
vpc <- NULL #vpc here means "variance per cluster"
for (i in 1:k) {
    kfit <- kmeans(tdm, i)
    vpc <- c(vpc, kfit$betweenss/kfit$totss)
}
vpc

plot(1:k, vpc, xlab = "# of clusters", ylab = "explained variance")


```

**It appears that after 3 clusters, the increase in variance explained slows down. Thus, I'll be going with 3 clusters.**

```{r}

kfit <- kmeans(tdm, 3)

#clustering means were given for each of the eight emotions...
kfit$centers

fviz_cluster(kfit, data = tdm,
             palette = c("deepskyblue", "cyan3", "gold1"), 
             geom = "point",
             ellipse = F,
             ellipse.type = "t", 
             ggtheme = theme_bw()
             )


kfit
```
```{r}
cluster_tdm <- cbind(tdm, kfit$cluster)
cluster_tdm
```


```{r}
#trying kmeans clustering with the two sentiments: negative and positive

kfit2 <- kmeans(tdm2, 3)

fviz_cluster(kfit2, data = tdm2,
             palette = c("#2E9FDF", "#00AFBB", "#E7B800"), 
             geom = "point",
              ellipse = F,
             ellipse.type = "t", 
             ggtheme = theme_bw()
             )

#I don't like how this looks, there's an outlier, love, that doesn't want to 
#conform to one cluster mean

```


## Artists

**Data Cleanup** 
```{r}
#*sigh* idk why dbWriteTable creates a column of row numbers
#table is loaded with an extra and useless column
artists_complete <- select(artists_complete,-c(1))

df  <- vector(mode = "list", length = 49)
names(df) <- artists_complete$artist_names

for (i in 1:49) {
  
  df[[i]] <- gsub("[\\(\\)]", "", unlist(regmatches(artists_complete$artist_songs[i],
                                            gregexpr("\\(.*?\\)", 
                                            artists_complete$artist_songs[i]))))
}

df


#############
###need to input code that will remove the phrases that are not lyrics


############
#the last thing to do is to remove unwanted punctuation

#this removes everything inside brackets, brackets included
artists_complete$artist_songs <- gsub("\\[.+?\\]", "", 
                                      artists_complete$artist_songs)

#now with parenthesis includes lyrics being sung...
#this removes all the parenthesis BUT without removing the text inside
artists_complete$artist_songs <- gsub("\\s*\\([^\\)]+\\)","", 
                                        artists_complete$artist_songs)


#This replaces everything that's not alphanumeric signs, space or apostrophe 
#with an empty string...yes please
artists_complete$artist_songs <- gsub("[^[:alnum:][:space:]']", "", 
                                      artists_complete$artist_songs)

```



**Sentiment Analysis: Artist Data**
