 ---
title: "Sentiment Analysis on OG Sonnets and Artists"
author: "Mariana Gonzalez Castro"
date: "5/22/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(RMySQL)
library(DBI)

library(dplyr)
library(stringr)

library(tm)
library(syuzhet)
library(wordcloud)

library(cluster)
library(factoextra)

library(ggplot2)
```


```{r}
drv <- dbDriver("MySQL")
xdbsock <- ""


#############
xdbuser <- Sys.getenv("MAS405_AWS_MARIANA_DB_ROUSER_USER")
xpw     <- Sys.getenv("MAS405_AWS_MARIANA_DB_ROUSER_PW")
xdbname <- Sys.getenv("MAS405_AWS_MARIANA_DB_ROUSER_DBNAME")
xdbhost <- Sys.getenv("MAS405_AWS_MARIANA_DB_ROUSER_HOST")
xdbport <- as.integer( Sys.getenv("MAS405_AWS_MARIANA_DB_ROUSER_PORT") )



con <-
  dbConnect(
    drv,
    user=xdbuser,
    password=xpw,
    dbname=xdbname,
    host=xdbhost,
    port=xdbport,
    unix.sock=xdbsock
  )


dbListTables(con)

original_sonnets <- dbGetQuery(con, "SELECT * FROM OG")

#dbWriteTable(con, name = "OG_Sonnets_complete", og_sonnets, overwrite=T)

artists_complete <- dbGetQuery(con, "SELECT * FROM Artists_noDuplicates")

dbDisconnect(con)




```

## Original Sonnets

**Data Cleanup** 
```{r}
#*sigh* Idk why dbWriteTable creates a column of row numbers
og <- select(original_sonnets,-c(1)) 

og[1,1] #it appears that the special characters are back again...so stubborn

#R, wtf is up with the column name? 
og <- rename(og, "og_sonnets" = "rep.NA..154.")

og <- 
  og %>% 
  mutate_at("og_sonnets", str_replace, "’", "\'") 

og_sonnets <- data.frame(matrix(ncol=1,nrow=154, 
                                 dimnames=list(NULL, "Sonnets")))

#I manually removed the punctuation except for apostrophes
n <- 154
for (i in 1:154) {
  og_sonnets[i,]<- gsub("[,.;:?!]", "", og[i,1])
  rbind(og_sonnets[i,])
} 

og_sonnets[1,1]

#capture.output(og_sonnets, file = "OG_Sonnets_clean2.txt")

#lapply(og_sonnets, function(x) write.table( data.frame(x), 'OG_Sonnets_clean3.csv'  , append= T, sep=',' ))







```


**Sentiment Analysis** 
og_sonnets is the dataframe we are working with. (I know I use too many names lol)
```{r}
#create an empty dataframe
emotions <- data.frame(matrix(ncol=10,nrow=0, dimnames=list(NULL, 
      c("anger", "anticipation", "disgust", "fear", "joy", "sadness", 
        "surprise", "trust", "negative", "positive"))))

n <- 154

#ran a for loop to conduct sentiment analysis to each individual sonnet
for (i in 1:n) {
  emotions[i,]<- get_nrc_sentiment(og_sonnets[i,1])
  rbind(emotions[i,])
}

head(emotions) 

#should write this into my db...at some point


```



```{r}
#Very ROUGH barplot 
s <- colSums(emotions)
ss <- s[c("anger", "anticipation", "disgust", "fear", "joy", "sadness", 
        "surprise", "trust")]
sss <- s[c("negative", "positive")]
barplot(ss,
        main = "Frequency of Each Emotion",
        las = 2,
        col = terrain.colors(15),
        ylim = c(0,700))
barplot(sss,
        main = "Frequency of Positive and Negative Sentiments",
        las = 2,
        col = rainbow(15),
        ylim = c(0, 1200))


```

```{r}
#visualize what words fell under the 8 emotion categories

all = c(
  paste(og_sonnets[emotions$anger > 0,], collapse=" "),
  paste(og_sonnets[emotions$anticipation > 0,], collapse=" "),
  paste(og_sonnets[emotions$disgust > 0,], collapse=" "),
  paste(og_sonnets[emotions$fear > 0,], collapse=" "),
  paste(og_sonnets[emotions$joy > 0,], collapse=" "),
  paste(og_sonnets[emotions$sadness > 0,], collapse=" "),
  paste(og_sonnets[emotions$surprise > 0,], collapse=" "),
  paste(og_sonnets[emotions$trust > 0,], collapse=" ")
)

all <- removeWords(all, stopwords("english"))

all <- removeWords(all, c("thi", "thee", "thou", "may", "still", "thus", 
                          "though", "can", "will", "hath", "doth", "thine", 
                          "like", "much", "let", "upon", "from", "dost", 
                          "shall", "thy", "yet"))
all <- stripWhitespace(all)
all <- removeNumbers(all)

# create corpus
corpus = Corpus(VectorSource(all))

# create term-document matrix
tdm = TermDocumentMatrix(corpus)
#
# convert as matrix
tdm = as.matrix(tdm)
#
# add column names
colnames(tdm) = c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 
                  'surprise', 'trust')
comparison.cloud(tdm, random.order=F,
                 title.colors = c("#00B2FF", "red", "#FF0099", "#6600CC", 
                                  "green", "orange", "blue", "brown"), 
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", 
                            "orange", "blue", "brown"),
                 title.size=1, max.words=400,scale=c(2, 0.4),rot.per=0.5)

```



```{r}
#something doesn't feel right...checking the sentiments now

sentiments = c(
  paste(og_sonnets[emotions$negative > 0,], collapse=" "),
  paste(og_sonnets[emotions$positive > 0,], collapse=" ")
)

sentiments <- removeWords(sentiments, stopwords("english"))

sentiments <- removeWords(sentiments, c("thi", "thee", "thou", "may", "still", "thus", "though", "can", "will", "hath", "doth", "thine", "like", "much", "let",
                                        "upon", "from", "dost", "shall", "thy", "yet"))
sentiments <- stripWhitespace(sentiments)
sentiments <- removeNumbers(sentiments)

# create corpus
corpus2 = Corpus(VectorSource(sentiments))

# create term-document matrix
tdm2 = TermDocumentMatrix(corpus2)
#
# convert as matrix
tdm2 = as.matrix(tdm2)
#
# add column names
colnames(tdm2) = c('negative', 'positive')
comparison.cloud(tdm2, random.order=F,
                 title.colors = c("red","#00B2FF"), 
                 colors = c("red","#00B2FF"),
                 title.size=1, max.words=400,scale=c(2, 0.4),rot.per=0.5)

```



```{r}
total <- rowSums(tdm)
termdoc <- cbind(tdm, total)
head(termdoc)

total2 <- rowSums(tdm2)
termdoc2 <- cbind(tdm2, total2)
head(termdoc2)

#findFreqTerms(m, lowfreq = 300)
#findMostFreqTerms(m)
```


## Clustering Algorithm Attempt

I want to attempt a k-means clustering and see what happens. I am going to first determine the ideal number of clusters by checking how much variance of the data would be explained with the total number of clusters. 

```{r}
#will be applying k-means clustering to the Term Document Matrix or tdm 
k <- 8
vpc <- NULL #vpc here means "variance per cluster"
for (i in 1:k) {
    kfit <- kmeans(tdm, i)
    vpc <- c(vpc, kfit$betweenss/kfit$totss)
}
vpc

plot(1:k, vpc, xlab = "# of clusters", ylab = "explained variance")


```

**It appears that after 3 clusters, the increase in variance explained slows down. Thus, I'll be going with 3 clusters.**

```{r}

kfit <- kmeans(tdm, 3)

#clustering means were given for each of the eight emotions...
kfit$centers

fviz_cluster(kfit, data = tdm,
             palette = c("deepskyblue", "cyan3", "gold1"), 
             #geom = "point",
             ellipse = F,
             ellipse.type = "t", 
             ggtheme = theme_bw()
             )


kfit
```
```{r}
cluster_tdm <- cbind(tdm, kfit$cluster)
cluster_tdm
```


```{r}
#trying kmeans clustering with the two sentiments: negative and positive

kfit2 <- kmeans(tdm2, 3)

fviz_cluster(kfit2, data = tdm2,
             palette = c("#2E9FDF", "#00AFBB", "#E7B800"), 
             geom = "point",
              ellipse = F,
             ellipse.type = "t", 
             ggtheme = theme_bw()
             )

#I don't like how this looks...
#there's an outlier, love, that doesn't want to conform to one cluster mean

```


## Artists

**Data Cleanup** 
```{r}
#*sigh* idk why dbWriteTable creates a column of row numbers
#table is loaded with an extra and useless column
artists_complete <- select(artists_complete,-c(1))

###this code will take all the non-lyrical strings contained in a set of 
#parenthesis and compile it into some vector of lists thing...trust me, you'll see
#
df  <- vector(mode = "list", length = 45)
names(df) <- artists_complete$Artist

for (i in 1:45) {
  
  df[[i]] <- gsub("[\\(\\)]", "", unlist(regmatches(artists_complete$Lyrics[i],
                                            gregexpr("\\(.*?\\)", 
                                            artists_complete$Lyrics[i]))))
}

head(df) 


#############
###need to input code that will remove the phrases that are not lyrics

#I looked through the lists and roughly 10 artists contained these wannabe lyrics
#Of those 10, about 17 wannabe lyrics were discovered and now must be eliminated

artists_complete <- 
  artists_complete %>% 
  mutate_at("Lyrics", str_remove_all, pattern = c("Verse 1|Chorus 2|Verse 3|Chorus 3|x2|vocal solo|Saxophone solo|fadeout|chorus|Repeat 4 times|bv=|scat singing|4x|x8|x7|x4 |2x")) 

#can run this line of code again to verify if the strings are gone
#I would check adele, she had "Verse 1, Chorus 2, Verse 3, and Chorus 3
#you'll find that those phrases are no longer there and what remains is just 
#empty quotations...it's like you can still feel its presence but it's GONE

df2  <- vector(mode = "list", length = 45)
names(df2) <- artists_complete$Lyrics

for (i in 1:45) {
  
  df2[[i]] <- gsub("[\\(\\)]", "", unlist(regmatches(artists_complete$Lyrics[i],
                                            gregexpr("\\(.*?\\)", 
                                            artists_complete$Lyrics[i]))))
}

df2[["adele"]]

############
#the last thing to do is to remove unwanted punctuation

#this removes everything inside brackets, brackets included
artists_complete$Lyrics <- gsub("\\[.+?\\]", "", 
                                      artists_complete$Lyrics)

#now with parenthesis that includes lyrics being sung...
#this removes all the parenthesis BUT without removing the text inside
artists_complete$Lyrics <- gsub("\\s*\\([^\\)]+\\)","", 
                                        artists_complete$Lyrics)


#This replaces everything that's not alphanumeric signs, space or apostrophe 
#with an empty string...yes please
artists_complete$Lyrics <- gsub("[^[:alnum:][:space:]']", "", 
                                      artists_complete$Lyrics)

```



**Sentiment Analysis: Artist Data**

```{r}
art_emotions <- data.frame(matrix(ncol=10,nrow=0, dimnames=list(NULL, 
      c("anger", "anticipation", "disgust", "fear", "joy", "sadness", 
        "surprise", "trust", "negative", "positive"))))

n <- 45

#ran a for loop to conduct sentiment analysis to each individual sonnet
for (i in 1:n) {
  art_emotions[i,]<- get_nrc_sentiment(artists_complete[i,2])
  rbind(art_emotions[i,])
}

art_emotions
```


```{r}
art_bar <- colSums(art_emotions)
art_barss <- art_bar[c("anger", "anticipation", "disgust", "fear", "joy", "sadness", 
        "surprise", "trust")]
art_barsss <- art_bar[c("negative", "positive")]
barplot(art_barss,
        main = "Frequency of Each Emotion",
        las = 2,
        col = terrain.colors(15),
        ylim = c(0, 4000))
barplot(art_barsss,
        main = "Frequency of Positive and Negative Sentiments",
        las = 2,
        col = rainbow(15),
        ylim = c(0, 7000))

```


```{r}
#visualize what words fell under the 8 emotion categories
#artists_complete <- select(artists_complete,-c(1))

art_all = c(
  paste(artists_complete[art_emotions$anger > 0,], collapse=" "),
  paste(artists_complete[art_emotions$anticipation > 0,], collapse=" "),
  paste(artists_complete[art_emotions$disgust > 0,], collapse=" "),
  paste(artists_complete[art_emotions$fear > 0,], collapse=" "),
  paste(artists_complete[art_emotions$joy > 0,], collapse=" "),
  paste(artists_complete[art_emotions$sadness > 0,], collapse=" "),
  paste(artists_complete[art_emotions$surprise > 0,], collapse=" "),
  paste(artists_complete[art_emotions$trust > 0,], collapse=" ")
)

art_all <- removeWords(art_all, stopwords("english"))

art_all <- removeWords(art_all, c("aint", "ooh", "thou", "never", "yeah", "hey", "though", "just", "will", "dont", "gonna", "can",                                                            "let", "thing", "every", "cause", "Since", "along",  "always", "many" , "eighteen", "hundred",
                                            "upon", "from", "nah", "aint", "now", "one", "two", "cant", "dont", "wont", "like", "much","yet"))
art_all <- stripWhitespace(art_all)
art_all <- removeNumbers(art_all)

# create corpus
art_corpus = Corpus(VectorSource(art_all))

# create term-document matrix
art_tdm = TermDocumentMatrix(art_corpus, control = list(wordLengths=c(0,Inf)))
#
# convert as matrix
art_tdm = as.matrix(art_tdm)
#
# add column names
colnames(art_tdm) = c('anger', 'anticipation', 'disgust', 'fear', 'joy', 'sadness', 
                  'surprise', 'trust')
comparison.cloud(art_tdm, random.order=F,
                 title.colors = c("#00B2FF", "red", "#FF0099", "#6600CC", 
                                  "green", "orange", "blue", "brown"), 
                 colors = c("#00B2FF", "red", "#FF0099", "#6600CC", "green", 
                            "orange", "blue", "brown"),
                 title.size=1, max.words=400, scale=c(2, 0.4), rot.per=0.5)

#barplot(art_tdm)

```



```{r}
#Dominique's code for Sentiment Analysis

sent_scores <- get_sentiment(og_sonnets$Sonnets)
summary(sent_scores)

sent_artists <- get_sentiment(artists_complete$Lyrics)
summary(sent_artists)


```
